\huge Tor's Usability for Censorship Circumvention

### 2016-04-06 pets2017-paper/pets2017-paper.tex
Use fifield@cs, not fifield@eecs, to match others.
refactor intro into intro and related work

  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@eecs.berkeley.edu}}

@@

\section{Introduction}
Tor is primarily known as the most widely used anonymity tool today. 
For this reason, user studies on Tor have been solely about the usability of Tor as an
anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
``stopping points'' in Tor Browser, documenting points when people would get frustrated enough
to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
Since then, Tor has had a lot of updates. There have been been no published usability evaluations of
Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
Lee and Fifield~\cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
5.1 and later. There has been no work done on Tor as a censorship circumvention tool.

Many features of Tor have not been evaluated through user
research --- such as advanced web tasks (e.g., accessing hidden services), the
configuration menu to connect to the Tor network, configuring automatic
updates, and identity/cookie management. Rather than selecting the features to
study in isolation, we decided to focus on an important use case of Tor browser: censorship circumvention. 
Internet censorship is pervasive across the world today~\cite{faris2008measuring}. 
Although Tor was not designed to be a censorship circumvention tool, users started
using it as one, since Tor's role as a proxy to anonymize
people also worked to circumvent censorship. Now, circumventing censorship is a
common use case for Tor, and current censorship circumvention methods are
incorporated into Tor, making it a viable censorship circumvention tool even in the face
of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason~\cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.

We believe that this is a great opportunity for user research. This study aims to understand of what is confusing about the configuration process and what find changes make the process easier. Our study consists of three stages. User interactions with the current interface in various censorship environments generated the problems we address in the study. User feedback and observations of users steered the design process for an improved configuration interface. User metrics, such as success rate and time to completion, measured how well the interfaces served their purpose.

@@

@@

\subsection{Censorship Today} 
Internet censorship is widespread throughout the world. Although there are corporations, parental controls, and other forms of censorship, the most common form of censorship is done by a nation-state power, usually without the consent of the people in that residing nation. Currently {\color {red} TODO} governments implement some sort of Internet censorship in their country. The most commonly censored categories of websites are {\color {red} TODO} ({\color {red} TODO}\%), {\color {red} TODO} ({\color {red} TODO}\%), {\color {red} TODO} ({\color {red} TODO}\%), {\color {red} TODO} ({\color {red} TODO}\%), and {\color {red} TODO} ({\color {red} TODO}\%).  Reactions from Internet censorship range from feeling safe that bad sites are blocked automatically for their citizens to being outraged that access to information and free speech have been infringed upon. The risks associated with circumventing Internet censorship, is largely based on the geographic location, how prevalent censorship circumvention is, and who you are.

@@

A heuristic evaluation is a rule-based evaluation that leverages standards
that have shown to work in the User Interface design 
community. We draw from Jacob Nielsen's ten heuristics ({\color {red} CITE THIS})
and other industry standards to form the following heuristic evaluation criteria: \\

@@

\subsection{Methodology} 
In this section, we talk about the details of our qualitative user study, such as the censorship environments we placed our users in, how we pre-screened and selected our participants, and the procedure for the experiment.

@@

@@

\section{Related Work} 
{\color {red} TODO}

\section {Acknowledgments}
{\color {red} Rowie for setting up Xlab, Ganesh for helping us redesign the Interface, Nima, Isa, Georg, and the UX team for giving feedback, and Cecile for reviewing the UI of circumvention tools.}

% Rowie
% Ganesh
% Nima, Isa, Georg, Tor UX team. 
% Cecile Basnage for review of the UI of circumvention tools.

>>>>

  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}

@@

\section{Introduction}

Although Tor ~/cite{dingledine2004tor} was not designed to be a censorship circumvention tool, users started
using it as one, since Tor's role as a proxy to anonymize
people also worked to circumvent censorship. Now, circumventing censorship is a
common use case for Tor, and current censorship circumvention methods are
incorporated into Tor, making it a viable censorship circumvention tool even in the face
of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason~\cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.

We believe that this is a great opportunity for user research. We have the opportunity to help users circumvent censorship more easily and provide them with extra security features, such as anonymity. Not only does improving the interface help the user trying to circumvent censorship, it helps other users who use Tor as an anonymity system by increasing the number of overall users ~\cite{dingledine2006anonymity}. This study aims to understand of what is confusing about the configuration process and what find changes make the process easier. Our study consists of three stages. User interactions with the current interface in various censorship environments generated the problems we address in the study. User feedback and observations of users steered the design process for an improved configuration interface. User metrics, such as success rate and time to completion, measured how well the interfaces served their purpose.

@@

\section{Related Work} 
There have been been no published usability evaluations of
Tor Browser since the 4.0 series, which introduced radical UI changes. 
The most recent usability effort is an unpublished pilot study  by Lee and Fifield~\cite {uxsprint} 
that tests the download, install, and  user interface of Tor Browser.  This study uncovered a number of bugs~\cite{uxsprint2015-tickets}. Changes made are reflected in series 5.1 and later.

There have been three published user studies on Tor to our knowledge. Clark et. al examines various deployment
options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
were satisfactory from a usability perspective. Fabian et. al show that Tor's added latency 
~\cite{dingledine2009performance} causes users
to be frustrated, cancel requests more often, and prevent user adoption. Norcie et. al found found that 
64\% of users are unable to continue with installation or browsing at least once due to difficulties.

Previous user studies have not focused on specific features in isolation, while we choose to focus our study on 
the configuration interface. The configuration interface in isolation is the censorship circumvention 
interface, as it guides users through setting up network components required to circumvent censorship. 
This study examines that interface, and effectively, the usability of Tor as a censorship circumvention tool.

@@

\subsection{Censorship Today} 
Internet censorship is widespread throughout the world ~\cite{faris2008measuring}. Although there are corporations, parental controls, and other forms of censorship, the most common form of censorship is done by a nation-state power, usually without the consent of the people in that residing nation. Currently {\color {red} TODO} governments implement some sort of Internet censorship in their country. The most commonly censored categories of websites are {\color {red} TODO} ({\color {red} TODO}\%), {\color {red} TODO} ({\color {red} TODO}\%), {\color {red} TODO} ({\color {red} TODO}\%), {\color {red} TODO} ({\color {red} TODO}\%), and {\color {red} TODO} ({\color {red} TODO}\%).  Reactions from Internet censorship range from feeling safe that bad sites are blocked automatically for their citizens to being outraged that access to information and free speech have been infringed upon. The risks associated with circumventing Internet censorship, is largely based on the geographic location, how prevalent censorship circumvention is, and who you are.

@@

A heuristic evaluation is a rule-based evaluation that leverages standards
that have shown to work in the User Interface design 
community. We draw from Jacob Nielsen's ten heuristics~\cite{nielsen1994heuristic}
and other industry standards to form the following heuristic evaluation criteria: \\

@@

\subsection{Methodology} 
In this section, we talk about the details of our qualitative user study, such as the inspection of the interface, censorship environments we placed our users in, how we pre-screened and selected our participants, and the procedure for the experiment.

\subsubsection{Inspection} 
A combination of usability inspection methods~\cite{nielsen1994usability}
 were used prepare for the user study. Two researchers conducted a pluralistic 
walkthrough and stepped through various censorship
scenarios, discussing which elements would be involved for that use case, and walking 
through the configuration process. After compiling all the possible paths through the 
interface {\color {red} digraph here?}, feature inspection was performed to list sequences
of features used to accomplish typical tasks, taking note of long sequences or cumbersome
steps. To focus our observations, a heuristic evaluation was performed to mark design issues 
that may cause confusion for users during our study.

@@

\section{Limitations} 
{\color {red} our study was only run on windows machines. our participants were not motivated like real users would be in real environments to succeed, but also may have been too motivated since they were getting paid. We didn't intentionally test the cases in which the user is required to configure a custom bridge or proxy. Our users were recruited from one geographic location, and their first language is English.}

@@

\section {Acknowledgments}
{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isa (?), Georg (?), and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}
